---
title: "My Final Project Template"
author: Emily McCray
subtitle: Subtitle here if desired
date: today
date-format: long
---

# Introduction

\[\~ 200 words\]

Fear of flying is incredibly common, despite airplanes being one of the safest mode of travel. The likelihood of being involved in a plane crash ... Plane crashes are much less frequent now than they were decades ago, when air travel was first becoming popular?

This decrease in crashes is partially attributed to advances in technology, but it is also owed to government policy changes (e.g., the FAA in the United States). Due to these differences in regulations around the world, do some countries have a greater number of commercial airline crashes than others?

Additionally, does the common causes crash (e.g., pilot error, mechanical issue) differ by country?

The goal of this project is to take a deeper dive into plane crash statistics to determine if certain areas of the world...

plane crashes have gone down (statistics say this is the safest way to travel)
take a deeper dive to see how the decline in plane crashes has differed among different countries

overall technological advancements have led to this decrease, but other factors such as policy may differ by country causing differences
questions to be answered are which countries historically have the most commercial plane crashes

of these countries, have any had a steeper decline (indicating greater improvement/safety standards) than others?

does the primary cause of crash (e.g., weather, mechanical failure, pilot error) differ among these countries?

hypothesized that larger countries with more air travel will have the most plane crashes, simply due to having a greater amount of flights)

also believed that certain countries (e.g., the US) will have a steeper decline in (I only know this bc I live here, but the US has not had a commercial airplane crash since 2009, which actually occurred right here in Buffalo) 


Clearly stated background and questions / hypotheses / problems being addressed. Sets up the analysis in an interesting and compelling way. Include figures if you like.

# Materials and methods

\[\~ 200 words\]

Narrative: Clear narrative description of the data sources and methods. Includes data from at least two sources that were integrated / merged in R.

Code: The code associated with the project is well organized and easy to follow. Demonstrates mastery of R graphics and functions.

Data: The underlying data are publicly accessible via the web and downloaded/accessed within the Rmd script. If you want to use your own data, you must make it available on a website (e.g. Figshare) so that others are able to re-run your code.

You can do bullets like this:

-   The first most important thing
-   The second most important thing
-   The third most important thing

You can do numbers like this:

1.  The first most important thing
2.  The second most important thing
3.  The third most important thing

See <http://rmarkdown.rstudio.com/> for all the amazing things you can do.

Here's my first code chunk.

```{r}
x=3+4
```

```{r}
#data https://data.ntsb.gov/avdata/FileDirectory/DownloadFile?fileID=C%3A%5Cavdata%5Cavall.zip
```


Refer to output in your narrative like this: x=`r x` .

Load any required packages in a code chunk (you may need to install some packages):

```

Add any additional processing steps here.

# Results

\[\~200 words\]

Tables and figures (maps and other graphics) are carefully planned to convey the results of your analysis. Intense exploration and evidence of many trials and failures. The author looked at the data in many different ways before coming to the final presentation of the data.

Show tables, plots, etc. and describe them.


```


```

### Dygraphs Example



```

# Conclusions

\[\~200 words\]

Clear summary adequately describing the results and putting them in context. Discussion of further questions and ways to continue investigation.

# References

All sources are cited in a consistent manner
